Visually pleasing knot projections

### 2023-02-02 inst/jma_rebuttal_2023_01_30.tex

A few comments on some rebuttals:

RE: Why use Bezier curves? : A key point, which should be mentioned in
the justification for Bezier curves, is that they interpolate their
end-points. This gives users a convenient, more direct control of
where these curve segments will appear than what they would get from
G2-continuous B-splines, which are only approximating their control
points.\textcolor{blue}{\\Fixed: sentence added to manuscript\\ \\}

RE: Why not place nodes at the crossing points? : Yes, this will
require a different, slightly more sophisticated drawing interface;
but this may then pay off heavily in a simpler, more efficient
optimization process.

For each crossing point, the user would see an orthogonal ``cross-hair"
that can be shifted and rotated as a whole.  In addition, there are
two parameters (handle-pairs) that control the ``velocities" of the two
strands through the crossing.  The optimization routine would
fine-tune these velocities to achieve matching curvature for the two
sequentially connected Bezier curves.

And, yes, if a crossing point falls on a line of mirror symmetry, the
crosshair would automatically be angled at 45 degrees with respect to
this line.  And if the knot has n-fold rotational symmetry, n such
cross hairs would be placed at the vertices of a regular n-gon.  (All
this is not such a ``nightmare" if it is properly considered from the
beginning.)

### 2023-02-02 inst/jma_knot.tex
start work on #79

\begin{itemize}
\item Curvature to be as smoothly changing as possible, with limited maximal curvature
\item Strands to cross at right angles
\item Crossing points to be separate from one another
\item Any symmetry desired in the knot should be enforced exactly, and be visually apparent
\end{itemize}

>>>>

\begin{description}
\item[Path clarity] The projection should clearly show the path of the
  knot, with no confusion or ambiguity in the visual representation.
\item[Visual continuity] Strands to be as smoothly changing as
  possible, with limited maximal curvature and no distracting features
\item[Crossing identification] Strands to cross at right angles if
  possible, as this admits a precise visual location and ready
  differentiation between overstrand and understrand
\item[Crossing spacing] The distance between crossings should be
  visually balanced to create a harmonious projection
\item[Symmetry] Any symmetry present in the knot (either rotational or
  mirror) should be enforced exactly, and be visually apparent
\end{description}
